Increasing prevalence of plant-fungal symbiosis across two centuries of environmental change

### 2024-09-18 Manuscript/endo_herbarium.tex
editing caption

	\begin{figure}[H]
		\centering
		\includegraphics[width = \linewidth]{../Plots/endo_status_map.png}
		\caption{\textbf{Endophyte presence/absence in specimens of each host species.} Points show collection locations colored according to whether the specimen contained endophytes ( E+; blue points) or did not contain endophytes (E-, tan points) and are faceted based on collection period.}
		\label{fig:endo_status_map}
	\end{figure}

>>>>

	\begin{figure}[H]
		\centering
		\includegraphics[width = \linewidth]{../Plots/endo_status_map.png}
		\caption{\textbf{Endophyte presence/absence in specimens of each host species.} Points show collection locations colored according to whether the specimen contained endophytes ( E+; blue points) or did not contain endophytes (E-, tan points). To visualize temporal change, the data are faceted before and after the median year of collection.}
		\label{fig:endo_status_map}
	\end{figure}
